---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

ARTS102 ggplotgui
==========

This is a fork of <https://github.com/gertstulp/ggplotgui> for use in teaching.

# Installation
```{r, eval=FALSE}
install.packages("ggplotgui")

# In order to install the most recent version of this package, you'll need to use the "devtools"-package
install.packages("devtools")
devtools::install_github("JoshuaDavidBlack/ggplotgui")

library("ggplotgui")
```

# Usage
Call ggplot_shiny() from within R.
```{r, eval=FALSE}
# You can call the function with and without passing a dataset
ggplot_shiny()
ggplot_shiny(mpg) # Passing ggplot's mpg dataset
```


There are four ways in which you can use data within this GUI:    
1. You can pass your dataframe through R, by using ggplot_gui(my_df)    
2. You can examine sample data (data 'mpg' from the ggplot2 package)    
3. You can upload your datafile in many different formats (e.g., csv,Excel)    
4. You can paste some data into a window (the data need to be "[tidy](http://tidyr.tidyverse.org/)")    


A ggplot-graph can be made through point and click (after data is loaded and through the plot tab).
Aesthetics of the graph can be changed with the tabs on the right hand side. 

